Long name of the paper

### 2018-08-21 anzjs2018/anzjs2018.tex
more words

Recieve vehicle updates ~30 seconds (but the actual update frequency varies continually, even for a single bus).
Key features of the data - position, trip, timestamp, etc.
Also note there is trip updates feed, but this is less useful (the arrival/departure times themselves haven't proved reliable).

@@

The real-time vehicle model that runs ... in real time?

>>>>

GTFS realtime allows developers to query the current positions of vehicles
in the transit network.
The data consists of the time $t_k$ that the observation was made,
the GPS position of the vehicle, $Y_k$, 
and some other information about the trip being serviced.
Vehicle positions are usually updated within 30~seconds,
but this can vary from 10~seconds to several minutes,
so there is often a lot of uncertainty about the trajectory
between two observations, particularly when there is a bus stop
or intersection between them.

Another complication with the Auckland Transport realtime feed is that
the buses are programmed to report their location when arriving at
bus stops and some major intersections.
Often these positions appear to be preemptive (i.e., that bus is almost there, 
but not quiet),
and subsequent observations place the bus \emph{behind} the stop or intersection.
This must therefore be accounted for in the model proposed in the next section.

@@

In order to estimate vehicle speed from a series of noisy GPS observations,
we need a model capable of overcoming several key problems:
varying update intervals, multimodality, assymetry, 
and some other artefacts such as mentioned in Section~\ref{sec:realtime_data}.
One estimation technique that suits itself well to this type of problem
is the particle filter, 
which has been used in several other bus modeling applications
\citep{Hans_2015}.
The primary advantage of this approach is that we need not make any 
unnecessary assumptions, particularly on the shape of the distributions 
as is the case in other commonly used methods such as the Kalman filter.
